---
title: "Potter Cove Carbon Budget"
author: "L.A.S."
date: "December 1, 2016"
output: html_document
---

## Estimation of phytoplankton standing stock 



```{r DataConversion, eval=TRUE}

load(".RData")

chla <- read.delim("../CarbonBudgetData/chla_mgdm3_PotterCove.dat")
require(dplyr)
chla <-  chla %>% mutate(chlaE1 = replace(chlaE1, chlaE1==0, NA),chlaE2 = replace(chlaE2, chlaE2==0, NA),chlaTot=(chlaE1+chlaE2)/2)

require(fitdistrplus)
chla1 <- as.numeric(na.omit(chla$chlaTot))
chla_dist <- descdist(chla1, discrete=FALSE, boot=500)


chla_dist$mean * 1e-3 * 55
chla_dist$max  * 1e-3 * 55
chla_dist$min  * 1e-3 * 55

```

* Mean Standing stock anual Chla µg/l mg/m2 40.12
      * SD 96.59
      * Min 1.50
      * Max 1042.64
      * Median 18.69
* mg -> 1e-3 g          
* µg chla -> 55 µg C 

* Mean phyto C g/m2 2.206862
* Max phyto C g/m2  57.3452
* Min phyto C g/m2  0.0826

```{r DataConversionPhyto, eval=TRUE}
require(dplyr)
# Anual average standing stock 
#
data <- tibble(box="Phyto",type="Stock",
                mean= round(chla_dist$mean,4) * 1e-3 * 55 ,
                max = round(chla_dist$max,4)  * 1e-3 * 55 ,
                min = round(chla_dist$min,4)  * 1e-3 * 55,
                sd =  round(chla_dist$sd,4)  * 1e-3 * 55)


# Production

# Data from Schloss, I. R., Ferreyra, G. A., & Curtosi, A. (1988). Phytoplankton prirnary production in Potter Cove, King George Island. In C. Wiencke, G. Ferreyra, W. E. Arntz, & C. Rinaldi (Eds.), The Potter Cove Coastal Ecosystem, Antarctica. Ber. Polarforsch. (Vol. 299, pp. 67–73).

# Producción (mg C m-2 día-1) de 91 a 478 media 236 para producción (para pasar a anual multiplicar por 180 dias). Ambos guarismos son de Schloss, Ferreyra, Curtosi. También aparecen en Tesis Schloss  48.68 g C m² año-1. 

# data <- data %>% mutate(type="Stock")
# data <- select(data, box,type,mean:sd)

data <- add_row(data, box="Phyto", type="Prod", 
                mean= 236*180/1000,
                max = 478*180/1000,
                min = 91*180/1000)

```

# Zoo plankton

* Garcia, M. D., Hoffmeyer, M. S., Abbate, M. C. L., Barría de Cao, M. S., Pettigrosso, R. E., Almandoz, G. O., … Schloss, I. R. (2016). Micro- and mesozooplankton responses during two contrasting summers in a coastal Antarctic environment. Polar Biology, 39(1), 123–137. https://doi.org/10.1007/s00300-015-1678-z

Units are  micro zoo µg/l C = -> 1e-06*1000 g m-3
Units are  meso zoo µg/m3 C = -> 1e-06 g m-3
Units are  macrozoo µg/m3 C = -> 1e-06 g m-3

conversion from m3 to Area --> Area of PC / Volume of PC above 30 m  = 0.1380776919 m2/m3



```{r DataConversionZoo, eval=TRUE}
# Anual average standing stock 
#
#

areaVol <- 0.1380776919

data <- add_row(data, box="MacroZoo", type="Stock",mean=(494940.97*1e-6*areaVol),
                          max=(4418890.21*1e-6*areaVol),
                          min=0)
data <- add_row(data, box="MesoZoo", type="Stock", mean=(22871.32*1e-6*areaVol),
                          max=(97133.15*1e-6*areaVol),
                          min=(171.21*1e-6*areaVol))

data <- add_row(data, box="MicroZoo", type="Stock", mean=(5.50*1e-3*areaVol),
                          max=(35.96*1e-3*areaVol),
                          min=(0.46*1e-3*areaVol))

data %>% mutate_if(is.numeric, round, digits=4) 


```

# Epibentos Sahade - Barnes 2006

Standard conversions 
@brey2010   C/Dry Mass 0.3587,  C/AFDM 0.4745

```{r DataConversionEPI, eval=TRUE}

require(dplyr)

data <- add_row(data, box="EpiBenthos",type="Stock", mean=(34.76),
                          max=(70.1286926365),
                          min=(2.3348481999))

save.image()

```



# Summer Macroalgae from @quartino2008a Extrapolated to the whole cove surface


@Quartino2008 g de peso seco de alga = 18,75 Joules

@Neveux2015 g de peso seco a Carbon = 0.28575

```{r DataConversionMACRO, eval=TRUE}

#
data <- add_row(data, box="Macroalgae", type="Stock",
                mean=round(83.95*0.286,4),
                          max=NA,
                          min=NA)

data <- add_row(data, box="Macroalgae", type="Prod", 
                mean=round(127.94*0.286,4),
                          max=NA,
                          min=NA)

data %>% mutate_if(is.numeric, round, digits=4) 

```


# Summer Meiofauna 0 - 5 cm
#

```{r DataConversionMEIO, eval=TRUE}

data <- add_row(data, box="InMacro", type="Stock", mean=16.93)

data <- add_row(data, box="InMeio", type="Stock", mean=6.4663)


```



## Bacterial standing stock


Mean 1e8 Cells/L
Max  1e9
min  1e6 

5 fgC/Cell

1 fg = 1e-15 g

1 L integrated in 30 m is 300

```{r BacterialStock, eval=TRUE}

temp <- (1e8* 5* 1e-15* 300)
tem1 <- (1e9* 5* 1e-15* 300)
tem2 <- (1e6* 5* 1e-15* 300)

data <- add_row(data, box="PelagicBact", type="Stock", mean=temp,max=tem1,min=tem2)

# Bacteria in Sediments 
# From @Pasotti2015a
# multiplied by the Proportion of soft sediments in PC 0.6864

data <- add_row(data, box="SedimentBact",type="Stock",
                mean=0.076 * 0.6864)

data %>% mutate_if(is.numeric, round, digits=4) 


save.image()
```

# Fish metabolism 

@Campbell2008
[units]  mg de O2 / 100 g x h

```{r fishMetabolism, eval=TRUE}


# Conversion molC/molO2 x 100 / 1000
# the average values of winter from april to november= 248 days (see fig 4)

temp_winter <- (1.48 * 0.375348450566896 * 100/1000)* 248
temp_sumer  <- (3.59 * 0.375348450566896 * 100/1000)* (365-248)


data <- add_row(data, box="Fish", type="Resp",
                mean=temp_winter+temp_sumer)

# Range: invierno 1 a 4 / verano 1,5 a 5

temp_winter <- (1 * 0.375348450566896 * 100/1000)* 248
temp_sumer  <- (1.5 * 0.375348450566896 * 100/1000)* (365-248)

data[13,]$min <- temp_winter+temp_sumer

temp_winter <- (4 * 0.375348450566896 * 100/1000)* 248
temp_sumer  <- (5 * 0.375348450566896 * 100/1000)* (365-248)

data[13,]$max <- temp_winter+temp_sumer

data %>% mutate_if(is.numeric, round, digits=4) 

save.image()
```

# Microphytobentos

@Atencio2008
```{r stockMPB, eval=FALSE}


temp <-c(5.04, 6.17, 3.07, 1.05, 3.6) # means
temp1 <-c(0.05, 0.05,0.14, 0.05, 0.5) # SD


# MPB in Sediments 
# 
# multiplied by the Proportion of soft sediments in PC 0.6864

temp <-weighted.mean(temp,1/temp1)   #[mg chla/ m2]

temp <- temp/1000*55*0.6864  # g/1000mg 55C/chla SoftSediment/TotalArea

data <- add_row(data, box="MPB", type="Stock",
                mean=temp)
data %>% mutate_if(is.numeric, round, digits=4) 

```

# DOC

@Ferreyra2008

DOC (µ Mol C/L)

micro Mol /L =  12 micro g /L = mili g /m3 = 1e-3 g/m3

conversion from m3 to Area --> Area of PC / Volume of PC above 30 m  = 0.1380776919 m2/m3

```{r stockDOC, eval=FALSE}

temp <- 39.15 * 12 * 1e-03 * 0.1380776919

data <- add_row(data, box="DOCWater",type="Stock", mean=(39.15*1e-3*areaVol),
                          max=(55.15*1e-3*areaVol),
                          min=(24.84*1e-3*areaVol))
#data<-data[-14,]


data <- add_row(data, box="POCWater",type="Stock", mean=(21.18*1e-3*areaVol),
                          max=(41.45*1e-3*areaVol),
                          min=(9.46*1e-3*areaVol))

data %>% mutate_if(is.numeric, round, digits=4) 

0.0076+.0057
save.image()
```


## Use LIM package to obtain unknown flows

```{r testLim, eval=FALSE}

require(LIM)
require(dplyr)
require(tidyr)
web.lim<-Setup("R/PotterCove_new.lim")
#web.lim<-Setup("R/PotterCove_test.lim")

#web.lim<-Setup("R/ScheldtIntertidal.input")



pars <- Ldei(web.lim)
webranges<- Xranges(web.lim)
xs <-Xsample(web.lim,jmp=10,iter=500)

dxs <- gather(data.frame(xs),flowname,flowvalue)
library(ggplot2)

flow_names <- unique(dxs$flowname) 
for(i in flow_names) 
  {
  print(ggplot(dxs %>% filter(flowname==i), aes(x = flowvalue)) + 
     #geom_histogram(bins = 10) + facet_wrap(~flowname, scales = 'free_x'))
     geom_density() + facet_wrap(~flowname, scales = 'free_x'))
  }  
# 
# p <- ggplot(dxs, aes(flowname,flowvalue)) + geom_point()
# p + stat_summary(fun.y = "mean", colour = "red", size = 1, geom = "point") +theme_bw()+coord_flip() + scale_y_log10()

mdxs <-  dxs %>% group_by(flowname) %>% summarise(mflow = mean(flowvalue), sdflow= sd(flowvalue), high= mflow+sdflow,low=mflow-sdflow ) %>% arrange(desc(mflow))
write.csv(mdxs,"Data/flowdata.csv")

require(viridis)
ggplot(mdxs, aes(flowname,mflow,colour=flowname)) + geom_point() + geom_linerange(aes(ymin = low, ymax = high)) +theme_bw()+coord_flip() + scale_y_log10() + scale_colour_viridis(discrete = T,guide=FALSE) 
ggsave("Figures/FluxesRanges2020.jpg",width=7,height=7,units="in",dpi=600)

## Solamente para PHY 
##
ggplot(mdxs %>% filter(grepl('PHY',flowname)), aes(flowname,mflow,colour=flowname)) + geom_point() + geom_linerange(aes(ymin = low, ymax = high)) + theme_bw()+coord_flip() + scale_colour_viridis(discrete = T,guide=FALSE) 

ggplot(mdxs %>% filter(grepl('BAC_s',flowname)), aes(flowname,mflow,colour=flowname)) + geom_point() + geom_linerange(aes(ymin = low, ymax = high)) + theme_bw()+coord_flip() + scale_colour_viridis(discrete = T,guide=FALSE) 

ggplot(mdxs %>% filter(grepl('BAC_w',flowname)), aes(flowname,mflow,colour=flowname)) + geom_point() + geom_linerange(aes(ymin = low, ymax = high)) + theme_bw()+coord_flip() + scale_colour_viridis(discrete = T,guide=FALSE) 

ggplot(mdxs %>% filter(grepl('FISH',flowname)), aes(flowname,mflow,colour=flowname)) + geom_point() + geom_linerange(aes(ymin = low, ymax = high)) + theme_bw()+coord_flip() + scale_colour_viridis(discrete = T,guide=FALSE) 

```

